High Resolution Identification of Protein-DNA Binding Events and Quality Control for ChIP-exo data

### 2015-11-12 rmarkdown/chip_exo_paper.Rnw
Changed the size of enrichment plots and added labels to plots

@@

\begin{figure}[h]
  \centering
  \includegraphics[width = .6\textwidth,page = 3 ]{../figs/for_paper/ChIPseqPET_ChIPexo_tagCount_comparison.pdf}
  % \includegraphics[width = .9\textwidth ,page = 3]{../figs/for_paper/MA_plot_fwd_bwd_by_seq.pdf}
  \caption{ A) ChIP signal in ChIP-exo was linearly related to that in
    PET ChIP-Seq data in the region with high ChIP tag counts. In
    contrast, there wer clear differences in their background
    distribution, where several of the background ChIP-exo regions
    were empty.}
  \label{fig:comp}
\end{figure}

% \[
% \mbox{FSR} = \frac{\mbox{Number of forward strand reads in region}}{\mbox{Total number of reads in region}}
% \]

>>>>

\begin{figure}[h!]
  \centering
  \includegraphics[width = .8\textwidth]{../figs/for_paper/Sig70_enrichment.pdf}
  \includegraphics[width = .8\textwidth,page =3]{../figs/for_paper/Local_SCC_indicator_by_strata.pdf}
  \caption{Enrichment and else}
  \label{fig:enrich}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width = .6\textwidth,page = 3 ]{../figs/for_paper/ChIPseqPET_ChIPexo_tagCount_comparison.pdf}
  % \includegraphics[width = .9\textwidth ,page = 3]{../figs/for_paper/MA_plot_fwd_bwd_by_seq.pdf}
  \caption{ A) ChIP signal in ChIP-exo was linearly related to that in
    PET ChIP-Seq data in the region with high ChIP tag counts. In
    contrast, there wer clear differences in their background
    distribution, where several ChIP-exo background regions were
    empty.}
  \label{fig:comp}
\end{figure}
